Reproducibility in Plant Pathology

### 2020-04-08 README.rmd
Update web url of personal site
Clean up README

[![Travis-CI Build Status](https://travis-ci.org/openplantpathology/Reproducibility_in_Plant_Pathology.svg?branch=master)](https://travis-ci.org/openplantpathology/Reproducibility_in_Plant_Pathology)
[![DOI](https://zenodo.org/badge/62676177.svg)](https://zenodo.org/badge/latestdoi/62676177)
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)

@@

> Sparks, A.H., Del Ponte, E.M., Everhart, S., Foster, Z., Grünwald, N. (YYYY). _Title of paper_. Name of journal/book <https://doi.org/xxx/xxx>

@@

> Sparks, A.H., Del Ponte, E.M., Everhart, S., Foster, Z.S.L., Grünwald, N. (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for 'Status and Best Practices for Reproducible Research In Plant Pathology'_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.5281/zenodo.1250665>

@@

<https://adamhsparks.netlify.com/>

>>>>

[![DOI](https://zenodo.org/badge/62676177.svg)](https://zenodo.org/badge/latestdoi/62676177)
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)

@@

> Sparks, A.H., Del Ponte, E.M., dos Santos Alves, K., Foster, Z., Grünwald, N. (YYYY). _Title of paper_. Name of journal/book <https://doi.org/xxx/xxx>

@@

> Sparks, A.H., Del Ponte, E.M., dos Santos Alves, K., Foster, Z., Grünwald, N. (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for 'Status and Best Practices for Reproducible Research In Plant Pathology'_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.5281/zenodo.1250665>

@@

<https://adamhsparks.com/>
